Some Graphical Realizations of Two-Row Specht Modules of Iwahori--Hecke Algebras of the Symmetric Group

### 2019-08-01 tex/Drafts/Final_Draft.tex
Final Draft Yay

\subsection{Sign subrepresentations for $e\nmid n+r+1$}
\label{kernel}

@@

  This entirely characterizes $M_{2n + r}^r$ in the case that $e > n + r + 1$.
  In the next section, we will give weaker characterizations of $M_{2n + r}^r$ in the case $e = n + r + 1$, where the representation s $M_{2n + r}^r$ and $S^{(n+r,n)}$ are reducible.

 \section{Sign subrepresentations}\label{Sign section}
 Recall $K:=K^r_{2n+r}$, defined in section \ref{kernel}, is the direct sum of all sign subrepresentations. In the previous section, we were not able to prove $M_{2n+r}^r\cong S^{(n+r,n)}$ for $e=n+r+1$ because we could not assume $K=0$. In particular, our proof of irreducibility failed.

 In this section, we prove that there is exactly one sign subrepresentation when $e=n+r+1$, thus $M_{2n+r}^r$ is reducible. We give an explicit basis for $K$, and explore how our approach may generalize to finding subrepresentations other $e$.

@@

 First let us formalize a useful property of sub-matchings.

@@

 	The map is clearly bijective. Thus it is sufficient to prove the following: $$\rho(T_{i+a-1}\sigma)=T_i\rho(\sigma)$$

 	As mentioned in the previous section, the action of a transposition $T_i$ can change at most 4 nodes, so we need to show that the transpositions end up changing the same nodes in the same way in  $\rho(T_{i+a-1}\sigma)$ and $T_i\rho(\sigma)$.

 	Suppose $\sigma(i+a-1)=s,\sigma(i+a)=t$. Then $(T_{i+a-1}\sigma)(i+a-1)=i+a$, $(T_{i+a-1}\sigma)(s)=t$, so $\rho(T_{i+a-1}\sigma)(i)=i+1$, $\rho(T_{i+a-1}\sigma)(s-a+1)=t-a+1$. Separately, $\rho(\sigma)(i)=s-a+1$ and $\rho(\sigma)(i+1)=t-a+1$, so $T_i\rho(\sigma)(i)=i+1$ and $T_i\rho(\sigma)(s-a+1)=t-a+1$ as desired. So the map is an isomorphism and the lemma is proved.
 \end{proof}

@@

 \begin{definition}
 	Recall $Q_i:=(q^i+...+q+1)/q^{i/2}(-1)^i$ (lemma \ref{Q alg}). For $a>0$ define $Q(0,b):=1$. For $b>a>0$ define $$\Q_b^a:=\frac{Q_{b-1}...Q_{b-a}}{Q_1...Q_{a-1}}$$

@@

 	I will refer to $x_\psi$ as the \textbf{coordinate function} of $\psi$.

@@

 	Let $M_{2n+r}^r$ be a crossingless matchings representation, and suppose $Q_1,...Q_{n+r-1},\not=0$. Let $w\in\cap\ker(1+T_i)$. MLOG the rainbow element $R$ has coordinate 1 in $w$ (by proposition \ref{rainbow nonzero}). Then the coordinate of any basis element $\psi\in M_{2n+r}^r$ in $w$ is $x_{\psi}(q)$.

@@

 \begin{proof}
 	Suppose $\psi(1)=a$. The proof is structured as follows: use proposition \ref{shifted rainbow coeffs} to find the coefficient of the basis element with $\lfloor a/2\rfloor$ humps then a rainbow element; use the same proposition in a reversed manner to find the coefficient of the basis element consisting of the rainbow for the first $a$ nodes, then the rainbow for the final $2n+r-a$ nodes; finally, we finish the proof through induction using lemma \ref{sub-matching isomorphism}.

 	\vspace{2mm}
 	By proposition \ref{shifted rainbow coeffs} the element $R_1:=R_{L,n+r-1}$ has coordinate $Q_{n+r-1}$ in $w$. Then $R_1(3,2n+r)$ is the rainbow element in  $M_{2(n-1)+r}^r$, so the element $R_2$ defined by $R_2(1,2):=R_1(1,2)$, $R_2(3,2n+r):=R_{L,n+r-2}\in M_{2(n-1)+r}^r$ has coordinate $Q_{n-1}Q_{n-2}$. Generally, define $R_i$ by $R_i(1,2(i-1)):=R_{i-1}(1,2(i-1))$, $R_i(2i-1,2n+r):=R_{L,n+r-i}\in M_{2(n-i+1)+r}^r$. Then the coefficient of $R_i$ is $Q_{n+r-1}...Q_{n+r-i}$. These elements are shown in figure 5.

@@

 		$\cbr{
 			\begin{gathered}
 			\GeneralizedMatching{8}{3/8, 4/7,5/6}{2}{1/1,2/2}{5/4}, \hspace{\cbasisspacing}
 			\GeneralizedMatching{8}{1/2, 5/8,6/7}{2}{3/1,4/2}{5/4}, 
 			\hspace{\cbasisspacing}
 			\GeneralizedMatching{8}{1/2, 3/4,7/8}{2}{5/1,6/2}{5/4}, \hspace{\cbasisspacing}
 			\end{gathered}}$ 
 		\caption{In order, the rainbow element, $R_1$, and $R_2$. The coordinate of the rainbow element is 1. The coordinate of $R_1$ is $Q_{4}$. The coordinate of $R_2$ is $Q_4Q_3$. Generally, $R_i$ is the element with $i$ humps then a rainbow element, and has coordinate $Q_{n+r-1}...Q_{n+r-i}$.}
 	\end{figure}

 	Now define basis elements $E_i$ by $E_i(2i+1,2n+r):=R_i(2i+1,2n+r)$, $E_i(1,2i):=R$, the appropriate rainbow element. By the same argument as above, if $E_i$ has coordinate $c$ in $w$, $R_i$ has coordinate $Q_{i-1}...Q_{1}c$. One way to make this more clear is to consider intermediate basis elements $\sigma_j^{E_i}$ defined by $\sigma_j^{E_i}(2i+1,2n+r):=E_i(2i+1,2n+r)$ and $\sigma_j^{E_i}(1,2i):=R_{L,j}$. Then the coordinates of $\sigma_j^{E_i}(2i+1,2n+r)$ in terms of the coordinate $c$ of $E_i$ are $Q_{i-1}...Q_{i-j}$, and $R_i=\sigma_{i-1}^{E_i}$.

@@

 	Note that the above logic only uses proposition \ref{shifted rainbow coeffs}, which requires only that a sub-matching be a rainbow element. So, suppose some basis element $\sigma$ has sub-matching $\sigma(s,t)=R$ with $n'$ nodes and $r'$ anchors, and that the coordinate of $\sigma$ in $w$ is $c$. Then it follows that the basis element $\theta_i$ defined by $\theta_i(1,s-1):=\sigma(1,s-1)$, $\theta_i(t+1,2n+r):=\sigma(t+1,2n+r)$, and $\theta_i(s,t):=E_i$ has coefficient $\Q^i_{n'+r'}c$. In other words, defining $Y_\psi$ with respect to the sub-matching $\sigma(s,t)$, the operation of finding the coordinate of $E_i$ given the coordinate of $R=\sigma(s,t)$ commutes with the isomorphism to $Y_\psi$.  An example is given in figure \ref{kernel induct characterization example}.

@@

 	Given $\psi\in M_{2n+r}^r$, if $\psi(1)=a$, we may find the coordinate of $E_{\lfloor a/2\rfloor}$ as before. Note that this operation commutes with any isomorphism defined by lemma \ref{sub-matching isomorphism}. Me may define $Y_{E_{\lfloor a/2\rfloor}}$ with respect to the sub-matching $E_{\lfloor a/2\rfloor}(2,a-1)$. By the inductive hypothesis, we may apply the algorithm to this sub-matching and commute with the isomorphism with $Y_{E_{\lfloor a/2\rfloor}}$. In this way, we find that the coordinate of $\widehat{\psi}$ defined by $\widehat{\psi}(1,a):=\psi(1,a)$ and $\widehat{\psi}(a+1,2n+r)=R$ is $x_{\psi(2,a-1)}(q)\Q^{\lfloor a/2\rfloor}_{n+r}=x_{\widehat{\psi}}(q)$. Similarly, define $Y_{\widehat{\psi}}$ with respect to the sub-matching $\widehat{\psi}(a+1,2n+r)$, and commute the algorithm with the isomorphism. In the same way, we obtain that the coordinate of $\psi\in Y_{\widehat{\psi}}$ is $x_{\psi(2,a-1)}(q)x_{\psi(a+1,2n+r)}(q)\Q^{\lfloor a/2\rfloor}_{n+r}=x_\psi(q)$ as desired.

@@

 	\begin{figure}
 		\def\cbasisspacing{1mm}
 		\begin{adjustbox}{width=\textwidth}
 			\GeneralizedMatching{14}{3/12,4/11,5/10,6/9,7/8,13/14}{2}{1/1,2/2}{12/4}, \hspace{\cbasisspacing}
 			\GeneralizedMatching{14}{1/2,3/4,5/6,9/12,10/11,13/14}{2}{7/1,8/2}{12/4}, \hspace{\cbasisspacing}
 			\GeneralizedMatching{14}{1/6,2/5,3/4,9/12,10/11,13/14}{2}{7/1,8/2}{12/4}
 		\end{adjustbox}

 		\caption{The figure on the left has sub-matching $R$ ignoring the last two nodes. The middle figure has submatching $R_3$ ignoring the last two nodes. The figure on the right has sub-matching $E_3$ also ignoring the last two nodes. Since the last two nodes have the same structure for all elements, if the coordinate of the first element is $c$, the coordinate of the second is $Q_6Q_5Q_4c$, and the coordinate of the third is $\frac{Q_6Q_5Q_4}{Q_1Q_2}c$.}

@@

 To verify the kernel element, we will need to know exactly which basis elements are mapped to a specific basis element by a given $(1+T_i)$. The next two lemmas help address this question.

 {\color{magenta} Move lemmas to a new appendix $\backslash$section.}
 \begin{lemma}
 	Take some basis element $\psi\in M_{2n+r}^r$.

@@

 		\item Suppose $\psi(a)=b$ for some $b>a+1$, and that $(1+T_i)\psi=(1+q)\psi$ for some $a<i<b-1$. Me then have a subrepresentation $\psi(a,b)$ and define $Y_\psi$ with respect to this subrepresentation. Then for all basis elements $\sigma$ such that $(1+T_i)\sigma=q^{1/2}\psi$, we have that $$\sigma\in Y_\psi$$.

 		\item Suppose $\psi$ has some anchor at position $u$, and $(1+T_i)\psi=(1+q)\psi$ for some $i>u$, we again have a subrepresentation $\psi(u,2n+r)$ and define $Y_\psi$ with respect to this subrepresentation. Then for all basis elements $\sigma$ such that $(1+T_i)\sigma=q^{1/2}\psi$, we have that $\sigma\in Y_\psi$ again.

@@

 \begin{proof}
 	This lemma follows from an observation I made in section \ref{two humps created}: a transposition can only create two arcs or an arc and an anchor.

@@

 \vspace{5mm}
 Me are now ready to prove existence of a kernel element. To prove this, we will show that if $w\in M_{2n+r}^r$ is as characterized above, the coordinate of any basis element in $(1+T_i)w$ is zero. This will split into various cases related to the previous lemmas.

 \vspace{5mm}
 \begin{theorem}
 	Suppose $e=n+r+1$. Then $\cap\ker(1+T_i)\not=0$.
 	\label{kernel existence}
 \end{theorem}

@@

 	Given $\psi\in (1+T_i)M_{2n+r}^r$ let $E_\psi\subset M_{2n+r}^r$ be the pre-image of $\psi$ under the action of $(1+T_i)$. To prove $w$ is in the kernel, we must show the following: 
 	\begin{equation}
 	(1+q)x_\psi(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi}q^{1/2}x_\sigma(q)=0\text{ for all basis elements }\psi
 	\label{weak kernel}
 	\end{equation}
 	Inductively, we assume this equation holds for basis elements in smaller representations $M_{2n'+r'}^{r'}$, but only for $q$ such that $e=n'+r'+1$. Clearly this is true in the base case. For the following proof we will need a slightly stronger inductive assumption. Take $\psi'\in M_{2n'+r'}^{r'}$, and suppose either that $\psi'(1)=2n'+r'$, and that $T_i\psi'=(1+q)\psi'$, $1<i<2n'+r'-1$, or that 1 is an anchor in $\psi$. Defining $E_{\psi'}$ as before, we assume

@@

 	Before exploring the cases, let us formally define $E_\psi$ to be the pre-image of $\psi$ under the action of $(1+T_i)$, and $E_{\psi(a,b)}$ to be the pre-image of $\psi(a,b)$ under action of $(1+T_{i-a+1})$:

 	\begin{enumerate}[label={case \arabic*:}]
 		\item Suppose $\psi\in (1+T_i)M_{2n+r}^r$ for some $i$, and that $\exists s,t$ such that $s<i<t-1$, $s>1$ or $t<2n+r$, and $\psi(s)=t$. Also suppose the leftmost anchor is at some index $u>t$, or that there are no anchors. Then we have a sub-matching $\psi(s,t)$, and by lemma \ref{preimage under hump} $E_\psi\subset Y_\psi$. Then, using corollary \ref{characterization generalization}, the following equality holds:

@@

 		Me have that $e>j$ for any $Q_j$ term appearing in the equation above, and $e>n'+r'$ for any sub-matching coordinate appearing above, so by corollary \ref{coeff nonzero}:

@@

 		$$(1+q)x_{\psi(s,t)}(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi}q^{1/2}x_{\sigma(s,t)}(q)=0$$

@@

 		Note that both corollary \ref{characterization generalization} and our inductive hypothesis \ref{strong kernel} still apply in this case, where we consider a left anchor instead of a matching. This allows the exact same logic from the proof of the first case to prove this case.
 		\\

 		It is important to note that, for both case 1 and case 2, the inductive hypothesis depends only on cases in which \ref{strong kernel} holds. Thus, if we show these cases rely on valid base cases, case 1 and 2 follow. This will be done in case 4.

 		\vspace{5mm}
 		\item Suppose $\psi\in (1+T_i)M_{2n+r}^r$ for some $i$, the leftmost anchor is at a position $u>i+1$ or there are no anchors, and $\nexists s,t$ such that $\psi(s)=t$ and $s<i<t-1$. Lemma \ref{preimage under nothing} characterizes all $\sigma\in E_\psi$. Me would like to prove the following for arbitrary $q$ where $e>n+r$:

@@

 		See figure \ref{case 3} for an example of this equality. Note that if $e=n+r+1$, $Q_{n+r}$ is the only zero component in the right side of this equation, so proving this equation is sufficient to prove case three.
 		\\

 		Me will prove this equality through yet another inductive proof, this time inducting on the number of top level humps, including the leftmost anchor.

>>>>

\subsection{Sign subrepresentations when $e\nmid n+r+1$}\,
\label{kernel}

$\ $

@@

  This entirely characterizes $M_{2n + r}^r$ in the case that $e > n + r + 1$.
  Next, we will give weaker characterizations of $M_{2n + r}^r$ in the case $e = n + r + 1$, where the representations $M_{2n + r}^r$ and $S^{(n+r,n)}$ are reducible.

 \section{Sign subrepresentations and possible extensions}\label{Sign section}
 Recall $K:=K^r_{2n+r}$, defined in section \ref{kernel}, is the direct sum of all sign subrepresentations. In the previous section, we were not able to prove $M_{2n+r}^r\simeq S^{(n+r,n)}$ for $e=n+r+1$ because we could not assume $K=0$. In particular, our proof of irreducibility failed.

 In this section, we prove that there is exactly one sign subrepresentation when $e=n+r+1$, thus $M_{2n+r}^r$ is reducible. We give an explicit basis for $K$, and explore how our approach may generalize to finding subrepresentations for other $e$.

 Note that we will use notation from section \ref{kernel} freely.

@@

 First let us formalize a useful property of sub-matchings. Namely, acting on sub-matchings is the same as acting on the corresponding matching.

@@

 	The map is clearly bijective. Thus it is sufficient to prove the following: $$\rho((1+T_{i+a-1})\sigma)=(1+T_i)\rho(\sigma)$$

 	As mentioned in the previous section, the action of a transposition $T_i$ can change at most 4 nodes, so we need to show that the transpositions end up changing the same nodes in the same way in  $\rho((1+T_{i+a-1})\sigma)$ and $(1+T_i)\rho(\sigma)$.

 	Suppose $\sigma(i+a-1)=s,\sigma(i+a)=t$. Then $((1+T_{i+a-1})\sigma)(i+a-1)=i+a$, $((1+T_{i+a-1})\sigma)(s)=t$, so $\rho((1+T_{i+a-1})\sigma)(i)=i+1$, $\rho((T_{i+a-1})\sigma)(s-a+1)=t-a+1$. Separately, $\rho(\sigma)(i)=s-a+1$ and $\rho(\sigma)(i+1)=t-a+1$, so $(1+T_i)\rho(\sigma)(i)=i+1$ and $(1+T_i)\rho(\sigma)(s-a+1)=t-a+1$ as desired. So the map is an isomorphism and the lemma is proved.
 \end{proof}

@@

 \begin{definition}
 	Recall $Q_i:=(q^i+...+q+1)/q^{i/2}(-1)^i$ (lemma \ref{Q alg}). For $b\geq 0$, define $\Q^0_b:=1$. For $b\geq a>0$ define $$\Q_b^a:=\frac{Q_{b-1}...Q_{b-a}}{Q_0...Q_{a-1}}$$

@@

 	I will refer to $x_\psi$ as the \emph{coordinate function} of $\psi$.

@@

 	Let $M_{2n+r}^r$ be a crossingless matchings representation, and suppose $Q_1,...Q_{n+r-1},\not=0$. Let $w\in\cap\ker(1+T_i)$. WLOG the rainbow element $R$ has coordinate 1 in $w$ (by proposition \ref{rainbow nonzero}). Then the coordinate of any basis element $\psi\in M_{2n+r}^r$ in $w$ is $x_{\psi}(q)$.

@@

 \begin{proof}
 	Suppose $\psi(1)=a$. The proof is structured as follows: use proposition \ref{shifted rainbow coeffs} to find the coefficient of the basis element with $\lfloor a/2\rfloor$ length two arcs then a rainbow element; use the same proposition in a reversed manner to find the coefficient of the basis element consisting of the rainbow for the first $a$ nodes, then the rainbow for the final $2n+r-a$ nodes; finally, we finish the proof through induction using lemma \ref{sub-matching isomorphism}.

 	\vspace{2mm}
 	By proposition \ref{shifted rainbow coeffs} the element $R_1:=R_{L,n+r-1}$ has coordinate $Q_{n+r-1}$ in $w$. Then $R_1(3,2n+r)$ defines a rainbow sub-matching, and is the rainbow element in  $M_{2(n-1)+r}^r$. Thus we may define the element $R_2$ by $R_2(1,2):=R_1(1,2)$, $R_2(3,2n+r):=R_{L,n+r-2}\in M_{2(n-1)+r}^r$. By the same proposition, $R_2$ has coordinate $Q_{n-1}Q_{n-2}$ in $w$. Generally, define $R_i$ by $R_i(1,2(i-1)):=R_{i-1}(1,2(i-1))$, $R_i(2i-1,2n+r):=R_{L,n+r-i}\in M_{2(n-i+1)+r}^r$. Then the coefficient of $R_i$ is $Q_{n+r-1}...Q_{n+r-i}$. These elements are shown in figure \ref{hump the rainbow}.

@@

 		$\cbr{
 			\begin{gathered}
 			\GeneralizedMatching{8}{3/8, 4/7,5/6}{2}{1/1,2/2}{5/4}, \hspace{\cbasisspacing}
 			\GeneralizedMatching{8}{1/2, 5/8,6/7}{2}{3/1,4/2}{5/4}, 
 			\hspace{\cbasisspacing}
 			\GeneralizedMatching{8}{1/2, 3/4,7/8}{2}{5/1,6/2}{5/4}, \hspace{\cbasisspacing}
 			\end{gathered}}$ 
 		\caption{In order, the rainbow element, $R_1$, and $R_2$. The coordinate of the rainbow element is 1. The coordinate of $R_1$ is $Q_{4}$. The coordinate of $R_2$ is $Q_4Q_3$. Generally, $R_i$ is the element with $i$ length two arcs then a rainbow element, and has coordinate $Q_{n+r-1}...Q_{n+r-i}$.}
 		\label{hump the rainbow}
 	\end{figure}

 	Now define the basis elements $E_i$ to be those basis elements that can be split into two rainbow sub-representations between nodes $2i$ $2i+1$, the first of which has no anchors. Formally, they are defined by $E_i(2i+1,2n+r):=R_i(2i+1,2n+r)$, $E_i(1,2i):=R\in M_{2i}^0$. By the same argument as above, if $E_i$ has coordinate $c$ in $w$, $R_i$ has coordinate $Q_{i-1}...Q_{1}c$. To see this, note that $E_i$ by definition has rainbow sub-matchings $E_i(1,2i)$, so we may apply proposition $\ref{shifted rainbow coeffs}$ to that sub-matching and, as above, sequentially move middle arcs out of the rainbow. We will eventually reach the point where our rainbow sub-matching only has two nodes, and the basis element that we arrive at has all length two arcs and then a rainbow element starting at node $2i+1$. This basis element is $R_i$. It is easiest to see this in figure \ref{kernel induct characterization example}.

@@

 	Note that the above logic only uses proposition \ref{shifted rainbow coeffs}, which requires only that the basis element has a rainbow sub-matching. So, suppose some basis element $\sigma$ has rainbow sub-matching $\sigma(s,t)=R$ with $n'$ nodes and $r'$ anchors, and that the coordinate of $\sigma$ in $w$ is $c$. Then it follows that the basis element $\vartheta_i$ defined by $\vartheta_i(1,s-1):=\sigma(1,s-1)$, $\vartheta_i(t+1,2n+r):=\sigma(t+1,2n+r)$, and $\vartheta_i(s,t):=E_i$ has coefficient $\Q^i_{n'+r'}c$. In other words, defining $Y_\sigma$ with respect to the rainbow sub-matching $\sigma(s,t)$, the operation of finding the coordinate of $E_i$ given the coordinate of $R=\sigma(s,t)$ commutes with the isomorphism to $Y_\sigma$.  An example is given in figure \ref{kernel induct characterization example}.

 	\begin{figure}
 		\def\cbasisspacing{1mm}
 		\begin{adjustbox}{width=\textwidth}
 			\GeneralizedMatching{14}{1/2,5/14,6/13,7/12,8/11,9/10}{2}{3/1,4/2}{12/4}, \hspace{\cbasisspacing}
 			\GeneralizedMatching{14}{1/2,3/4,5/6,7/8,12/13,11/14}{2}{9/1,10/2}{12/4}, \hspace{\cbasisspacing}
 			\GeneralizedMatching{14}{1/2,3/8,4/7,5/6,12/13,11/14}{2}{9/1,10/2}{12/4}
 		\end{adjustbox}

 		\caption{The figure on the left has sub-matching $R$ ignoring the first two nodes. The middle figure has submatching $R_3$ ignoring the first two nodes. The figure on the right has sub-matching $E_3$ also ignoring the first two nodes. Since the first two nodes have the same structure for all elements, if the coordinate of the first element is $c$, the coordinate of the second is $Q_6Q_5Q_4c$, and the coordinate of the third is $\frac{Q_6Q_5Q_4}{Q_1Q_2}c$.}

@@

 	Given $\psi\in M_{2n+r}^r$, if $\psi(1)=a$, we may find the coordinate of $E_{\lfloor a/2\rfloor}$ as before. Note that this operation commutes with any isomorphism defined by lemma \ref{sub-matching isomorphism}. We may define $Y_{E_{\lfloor a/2\rfloor}}$ with respect to the rainbow sub-matching $E_{\lfloor a/2\rfloor}(2,a-1)$. By the inductive hypothesis, we may apply the algorithm to this sub-matching and commute with the isomorphism with $Y_{E_{\lfloor a/2\rfloor}}$. In this way, we find that the coordinate of $\widehat{\psi}$ defined by $\widehat{\psi}(1,a):=\psi(1,a)$ and $\widehat{\psi}(a+1,2n+r)=R$ is $x_{\psi(2,a-1)}(q)\Q^{\lfloor a/2\rfloor}_{n+r}=x_{\widehat{\psi}}(q)$. Similarly, define $Y_{\widehat{\psi}}$ with respect to the rainbow sub-matching $\widehat{\psi}(a+1,2n+r)$, and commute the algorithm with the isomorphism. In the same way, we obtain that the coordinate of $\psi\in Y_{\widehat{\psi}}$ is $x_{\psi(2,a-1)}(q)x_{\psi(a+1,2n+r)}(q)\Q^{\lfloor a/2\rfloor}_{n+r}=x_\psi(q)$ as desired.

@@

@@

 Now we must verify that the kernel element defined in proposition \ref{kernel characterization} is indeed an element of the kernel when $e=n+r+1$. To do this, we will need to know exactly which basis elements $\sigma$ are mapped to a specific basis element $\psi$ by a given $(1+T_i)$ for all $\psi$. The next two lemmas help address this question.

 \begin{lemma}
 	Take some basis element $\psi\in M_{2n+r}^r$.

@@

 		\item Suppose $\psi(a)=b$ for some $b>a+1$, and that $(1+T_i)\psi=(1+q)\psi$ for some $a<i<b-1$. We then have a subrepresentation $\psi(a,b)$ and may define $Y_\psi$ with respect to this subrepresentation. Then for all basis elements $\sigma$ such that $(1+T_i)\sigma=q^{1/2}\psi$, we have that $$\sigma\in Y_\psi$$.

 		\item Suppose $\psi$ has some anchor at position $u$, and $(1+T_i)\psi=(1+q)\psi$ for some $i>u$. We again have a subrepresentation $\psi(u,2n+r)$ and may define $Y_\psi$ with respect to this subrepresentation. Then for all basis elements $\sigma$ such that $(1+T_i)\sigma=q^{1/2}\psi$, we have that $\sigma\in Y_\psi$ again.

@@

 \begin{proof}
 	This lemma follows from a note I made in section \ref{two humps created}: a transposition can only alter two existing matchings.

@@

 \vspace{5mm}
 We are now ready to prove existence of a kernel element. To prove this, we will show that if $w\in M_{2n+r}^r$ is as characterized in proposition \ref{kernel characterization}, the coordinate of any basis element in $(1+T_i)w$ is zero. This will split into various cases related to the previous lemmas.

 \vspace{5mm}
 \begin{theorem}
 	Suppose $e=n+r+1$. Then $K\not=0$.
 	\label{kernel existence}
 \end{theorem}

@@

 	Given $\psi\in (1+T_i)M_{2n+r}^r$ let $E_\psi\subset M_{2n+r}^r$ be the pre-image of $\psi$ under the action of $(1+T_i)$. To prove $w$ is in the kernel, we must show the following: 
 	\begin{equation}
 	(1+q)x_\psi(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi}q^{1/2}x_\sigma(q)=0\text{ for all basis elements }\psi
 	\label{weak kernel}
 	\end{equation}
 	Inductively, we assume this equation holds for basis elements in smaller representations $M_{2n'+r'}^{r'}$, but only for $q$ such that $e=n'+r'+1$. Clearly this is true in the base case. For the following proof we will need a slightly stronger inductive assumption. Take $\psi'\in M_{2n'+r'}^{r'}$, and suppose either that $\psi'(1)=2n'+r'$, and that $(1+T_i)\psi'=(1+q)\psi'$, $1<i<2n'+r'-1$, or that 1 is an anchor in $\psi'$ and $(1+T_i)\psi'=(1+q)\psi'$, $1<i$. Defining $E_{\psi'}$ as before, we assume

@@

 	Before exploring the cases, let us formally define $E_\psi$ to be the pre-image of $\psi$ under the action of $(1+T_i)$, and, given some sub-matching $\psi(a,b)$ where $a\leq i<b$, $E_{\psi(a,b)}$ to be the pre-image of $\psi(a,b)$ under action of $(1+T_{i-a+1})$:

 	\begin{enumerate}[label={\textit{Case \arabic*.}}]
 		\item Suppose $\psi\in (1+T_i)M_{2n+r}^r$ for some $i$, and that there exist $s,t$ such that $s<i<t-1$, $s>1$ or $t<2n+r$, and $\psi(s)=t$. Also suppose the leftmost anchor is at some index $u>t$, or that there are no anchors. Then we have a sub-matching $\psi(s,t)$, and by lemma \ref{preimage under hump} $E_\psi\subset Y_\psi$. Then, using corollary \ref{characterization generalization}, the following equality holds:

@@

 		We have that $e>j$ for any $Q_j$ term appearing in the equation above, and $e>n'+r'$ for any sub-matching coordinate appearing above, so by corollary \ref{coeff nonzero}:

@@

 		$$(1+q)x_{\psi(s,t)}(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi}q^{1/2}x_{\sigma(s,t)}(q)=0\text{.}$$

@@

 		Note that both corollary \ref{characterization generalization} and our inductive hypothesis \ref{strong kernel} still apply in this case, where we consider a left anchor instead of a matching. The algebra is identical, and an analogous argument proves Case 2. This illustrates the isotopy shown in diagram \ref{Branching commutative diagram}.
 		\\

 		It is important to note that, for both Case 1 and Case 2, the inductive hypothesis depends only on cases in which \ref{strong kernel} holds. Thus, if we show these cases rely on valid base cases, Case 1 and Case 2 follow. This will be done in Case 4.

 		\vspace{5mm}
 		\item Suppose $\psi\in (1+T_i)M_{2n+r}^r$ for some $i$, the leftmost anchor is at a position $u>i+1$ or there are no anchors, and $\nexists s,t$ such that $\psi(s)=t$ and $s<i<t-1$. Lemma \ref{preimage under nothing} characterizes all $\sigma\in E_\psi$. We would like to prove the following for arbitrary $q$ where $e>n+r$:

@@

 		See figure \ref{case 3} for an example of this equality. Note that if $e=n+r+1$, $Q_{n+r}$ is the only zero component in the right side of this equation, so proving this equation is sufficient to prove Case 3.
 		\\

 		We will prove this equality through yet another inductive proof, this time inducting on the number of top level arcs, including the leftmost anchor.
